### 2014-12-04 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo in section label

The results of the simulation are discussed in the following sections. Section~\ref{sec:simulated_flow_path} addresses the results of the simulation as they relate to the flow path that was established in the interior stairwell. Section~\ref{sec:assessing_the_hazard} examines the simulation results as they relate to the hazardous conditions and exposure temperatures in the interior stairwell. Section~\ref{sec:tactical_condsiderations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.

@@

\section{Tactical Considerations}
\label{sec:tactical_condsiderations}

>>>>

The results of the simulation are discussed in the following sections. Section~\ref{sec:simulated_flow_path} addresses the results of the simulation as they relate to the flow path that was established in the interior stairwell. Section~\ref{sec:assessing_the_hazard} examines the simulation results as they relate to the hazardous conditions and exposure temperatures in the interior stairwell. Section~\ref{sec:tactical_considerations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.

@@

\section{Tactical Considerations}
\label{sec:tactical_considerations}
